TITLE

### 2021-02-26 outputs/Paper.Rmd
citation updates

[Appendix C](#appendixC) shows screen captures of the online version of the survey.In addition, we consulted several open datasets about the health inspection from each region. (CITATION)

>>>>

[Appendix C](#appendixC) shows screen captures of the online version of the survey.In addition, we consulted several open datasets about the health inspection from each region, including Peel[@citePeel], Halton[@citeHalton], York [@citeYork], Durham [@citeDurham], and Toronto [@citeToronto].
